\documentclass[12pt]{article}

% Packages
\usepackage[margin=1in]{geometry}
\usepackage{longtable}
\usepackage{array}
\usepackage{hyperref}
\usepackage{setspace}

\hypersetup{
    colorlinks=true,
    linkcolor=blue,
    urlcolor=blue
}

\begin{document}

%========================
% COVER PAGE
%========================
\begin{titlepage}
    \centering
    \vspace*{2cm}
    {\LARGE \textbf{Software Requirements Specification (SRS)}\par}
    \vspace{1.5cm}
    {\large Project: \textbf{Lab Activity 14}\par}
    \vspace{0.5cm}
    {\large Team Name: \textbf{Tommy W., Nadia H., Damarion M.P, Samantha V.M, Stephany C.P}\par}
    \vspace{0.5cm}
    {\large Group Number: \textbf{4}\par}
    \vspace{0.5cm}
    {\large Version: \textbf{1.0}\par}
    \vfill
    {\large Date: \textbf{December 5, 2025}\par}
    \vspace{2cm}
\end{titlepage}

%========================
% TABLE OF CONTENTS
%========================
\tableofcontents
\newpage

%========================
% VERSION DESCRIPTION
%========================
\section*{Version Description}
\addcontentsline{toc}{section}{Version Description}

\begin{longtable}{|>{\centering\arraybackslash}m{3cm}|
                      >{\arraybackslash}m{7cm}|
                      >{\centering\arraybackslash}m{3cm}|}
    \hline
    \textbf{Version} & \textbf{Description} & \textbf{Date} \\
    \hline
    1.0 & Initial SRS for Snapshot 1. Includes introduction, external interface requirements, legal and ethical considerations, and glossary. & December 5, 2025 \\
    \hline
\end{longtable}

\newpage

%========================
% 1. INTRODUCTION
%========================
\section{Introduction}

\subsection{Purpose of the Document}
The purpose of this Software Requirements Specification (SRS) is to describe all functional and non-functional requirements for the \textit{Lab Activity 14} system. It establishes what the software will do, how users will interact with it, and the constraints it must follow.

\bigskip

\noindent\textbf{Added Note from Group:}  
“Can you do step 5 for me. So project name would be Lab Activity 14. Team name here would be be Tommy W., Nadia H. Damarion M.P, Samantha V.M, Stephany C.P. Group number is 4 and the date is December 5 2025.”

\subsection{Intended Audience}
This document is intended for:
\begin{itemize}
    \item Stakeholders and students reviewing system expectations.
    \item Developers implementing system features.
    \item Instructors evaluating project completeness.
\end{itemize}

\subsection{Overview of the Software}
The \textbf{Lab Activity 14} software represents an academic exercise focused on generating professional documentation using LaTeX. It outlines requirements and design elements of a simple structured system used in software engineering courses.

\newpage

%========================
% 2. EXTERNAL INTERFACE REQUIREMENTS
%========================
\section{External Interface Requirements}

\subsection{User Interface}
\begin{itemize}
    \item The system provides a simple, easy-to-navigate interface.
    \item Users can select actions and navigate through menus.
    \item Clear prompts and forms enable user input.
\end{itemize}

\subsection{Software Interfaces}
\begin{itemize}
    \item The system may connect to a database for storing data.
    \item APIs can be used for authentication or external services.
    \item Data is exchanged in common formats such as JSON or form data.
\end{itemize}

\newpage

%========================
% 3. LEGAL AND ETHICAL CONSIDERATIONS
%========================
\section{Legal and Ethical Considerations}

\subsection{Data Storage and Privacy}
\begin{itemize}
    \item Minimal user data is collected.
    \item Sensitive information is protected using standard security practices.
    \item User access is restricted where necessary.
\end{itemize}

\subsection{Legal and Ethical Issues}
\begin{itemize}
    \item Users must be informed about what information is used or stored.
    \item Systems must comply with general data ethics and privacy expectations.
    \item Unauthorized data use or sharing is prohibited.
\end{itemize}

\newpage

%========================
% 4. GLOSSARY
%========================
\section{Glossary}

\begin{longtable}{|>{\centering\arraybackslash}m{3cm}|
                      >{\arraybackslash}m{9cm}|}
    \hline
    \textbf{Acronym} & \textbf{Definition} \\
    \hline
    UI & User Interface \\
    \hline
    API & Application Programming Interface \\
    \hline
    DB & Database \\
    \hline
    SRS & Software Requirements Specification \\
    \hline
    SDD & Software Design Document \\
    \hline
\end{longtable}

\end{document}
