\documentclass[12pt]{article}
\usepackage{geometry}
\geometry{margin=1in}

\title{Snapshot 1 Objectives \\ Intelligent Document Processing \& Case File Search System}
\author{Group 4: Tommy Works, Nadia Hernandez, Damarrion Morgan-Harper,\\
Samantha Moncada, Stephany Portillo}
\date{December 2025}

\begin{document}
\maketitle

\section*{Overview}
Snapshot 1 establishes the foundation of the project. The goal of this phase is to set up all core infrastructure, documentation, repository structure, and tools needed for future development. This snapshot includes project planning, environment setup, and preparation of all initial components.

\section*{Snapshot 1 Objectives}
\begin{itemize}
    \item Set up the GitHub repository with the required folder structure (backend, frontend, docs).
    \item Create initial project documentation (SRS, SDD, User Manual, Design Spec).
    \item Establish the Docker environment:
    \begin{itemize}
        \item Create \texttt{docker-compose.yml} with backend, database, and frontend placeholders.
        \item Build backend \texttt{Dockerfile}.
        \item Add backend \texttt{.env} configuration.
        \item Successfully run containers through Docker Desktop.
    \end{itemize}
    \item Prepare backend folder and initial API scaffolding.
    \item Prepare frontend folder for later development.
    \item Create Jira project and add Snapshot 1 tasks for Sprint 1.
    \item Add initial bug list to Jira for later TestRail integration.
    \item Draft first version of the workflow diagram.
\end{itemize}

\section*{Completion Summary}
Snapshot 1 has been successfully completed. All foundational files, Docker environment components, and documentation structures are in place. The development environment is stable and ready for the implementation of core features in Snapshot 2, including PDF upload, metadata extraction (basic or simulated), and database storage.

\section*{Next Steps (Snapshot 2 Preview)}
\begin{itemize}
    \item Build backend file upload API.
    \item Implement basic or simulated metadata extraction.
    \item Store extracted metadata in PostgreSQL.
    \item Implement search functionality.
    \item Update SDD, SRS, and User Manual for new features.
    \item Create TestRail Snapshot 2 test run documentation.
\end{itemize}

\end{document}

