\documentclass[12pt]{article}
\usepackage{geometry}
\geometry{margin=1in}

\title{Snapshot 4 Objectives \\ Intelligent Document Processing \& Case File Search System}
\author{Group 4: Tommy Works, Nadia Hernandez, Damarrion Morgan-Harper,\\
Samantha Moncada, Stephany Portillo}
\date{December 2025}

\begin{document}
\maketitle

\section*{Overview}
Snapshot 4 represents the final development phase of the Intelligent Document Processing \& Case File Search System. This phase focuses on polishing the system, finalizing documentation, completing the last set of TestRail results, and adding any final refinements that improve overall functionality and user experience. Snapshot 4 also includes the required reflection on completed work and proposed future enhancements.

\section*{Snapshot 4 Objectives}

\begin{itemize}
    \item Finalize all implemented features introduced in previous snapshots:
    \begin{itemize}
        \item Document upload and metadata extraction.
        \item Database storage and retrieval.
        \item Search functionality and filtering.
        \item Error handling and backend stability.
    \end{itemize}

    \item Improve and refine the user interface:
    \begin{itemize}
        \item Clean up layout, spacing, and component organization.
        \item Improve clarity of upload and search instructions.
        \item Provide meaningful success and error messages.
    \end{itemize}

    \item Perform final system integration testing:
    \begin{itemize}
        \item Ensure that all containers (frontend, backend, database) function correctly together under Docker Compose.
        \item Validate that uploads, metadata extraction, and search operations work consistently across multiple test cases.
        \item Address any bugs or inconsistencies discovered during testing.
    \end{itemize}

    \item Update documentation across all required files:
    \begin{itemize}
        \item Final updates to the SDD and SRS.
        \item Add final changes to the Design Spec, especially any modification to dependencies, UI components, or logic paths.
        \item Complete the User Manual and ensure instructions match the final system behavior.
    \end{itemize}

    \item Create and upload the final Snapshot 4 TestRail report:
    \begin{itemize}
        \item Include results from all executed test cases.
        \item Document pass/fail status and explanations for inconsistencies.
        \item Provide a final coverage summary.
    \end{itemize}

    \item Complete the final project reflection:
    \begin{itemize}
        \item Summarize what was completed successfully across all snapshots.
        \item Discuss challenges encountered and how they were addressed.
        \item Document lessons learned as a development team.
    \end{itemize}

\end{itemize}

\section*{Completion Summary}
By the end of Snapshot 4, the system is fully implemented, functioning, and documented. All four snapshots together demonstrate consistent progress in planning, development, testing, and refinement. The project now includes an operational document processing pipeline, metadata extraction workflow, search interface, and comprehensive user documentation—all running in a Dockerized environment.

\section*{Future Work}
Although the system meets the academic requirements for the course, several enhancements could be implemented in the future to improve real-world functionality:

\begin{itemize}
    \item Integrate true AI-powered metadata extraction (e.g., Box AI, AWS Textract, Tesseract OCR).
    \item Add authentication and role-based user access control.
    \item Enable bulk document uploads and batch processing.
    \item Add analytics dashboards for document statistics, case trends, or processing errors.
    \item Improve UI design with charts, previews, or interactive search filters.
    \item Build automated CI/CD pipelines to deploy updates more efficiently.
\end{itemize}

\section*{Final Reflection}
The team successfully designed, implemented, and tested a functional Intelligent Document Processing \& Case File Search System. Each snapshot contributed a critical component: system planning, upload workflow, metadata extraction, search functionality, and final refinements. Working as a team allowed us to divide responsibilities efficiently and build a complete project with coordinated documentation, Docker integration, and testing procedures.

\end{document}
