\documentclass[12pt]{article}

% Packages
\usepackage[margin=1in]{geometry}
\usepackage{longtable}
\usepackage{array}
\usepackage{hyperref}
\usepackage{setspace}

\hypersetup{
    colorlinks=true,
    linkcolor=blue,
    urlcolor=blue
}

\begin{document}

%========================
% COVER PAGE
%========================
\begin{titlepage}
    \centering
    \vspace*{2cm}
    {\LARGE \textbf{Software Requirements Specification (SRS)}\par}
    \vspace{1.5cm}
    {\large Project: \textbf{Lab Activity 14}\par}
    \vspace{0.5cm}
    {\large Team Name: \textbf{Tommy W., Nadia H., Damarion M.P, Samantha V.M, Stephany C.P}\par}
    \vspace{0.5cm}
    {\large Group Number: \textbf{4}\par}
    \vspace{0.5cm}
    {\large Version: \textbf{1.0}\par}
    \vfill
    {\large Date: \textbf{December 2025}\par}
    \vspace{2cm}
\end{titlepage}

%========================
% TABLE OF CONTENTS
%========================
\tableofcontents
\newpage

%========================
% VERSION DESCRIPTION
%========================
\section*{Version Description}
\addcontentsline{toc}{section}{Version Description}

\begin{longtable}{|>{\centering\arraybackslash}m{3cm}|
                      >{\arraybackslash}m{7cm}|
                      >{\centering\arraybackslash}m{3cm}|}
    \hline
    \textbf{Version} & \textbf{Description} & \textbf{Date} \\
    \hline
    1.0 & Initial SRS for Snapshot 1. Includes introduction, external interface requirements, legal and ethical considerations, and glossary. & December 5, 2025 \\
    \hline
    2.0 & Added functional and non-functional requirements for Snapshot 2. & December 7, 2025 \\
    \hline
    3.0 & Expanded system workflows and interface requirements for Snapshot 3. & December 9, 2025 \\
    \hline
    4.0 & Final updates for Snapshot 4, including legal updates and completed requirements. & December 11, 2025 \\
    \hline
\end{longtable}

\newpage

%========================
% 1. INTRODUCTION
%========================
\section{Introduction}

\subsection{Purpose of the Document}
The purpose of this Software Requirements Specification (SRS) is to describe the functional and non-functional requirements for the Intelligent Document Processing \& Case File Search System. It explains how the software will upload case PDFs, extract metadata, store it in a database, and allow users to search stored case information.

\subsection{Intended Audience}
This document is intended for:
\begin{itemize}
    \item Developers implementing frontend, backend, and database features.
    \item Instructors evaluating project completeness and correctness.
    \item Students reviewing system functionality expectations.
\end{itemize}

\subsection{Overview of the Software}
The software provides:
\begin{itemize}
    \item A document upload interface
    \item Automated metadata extraction (basic/simulated)
    \item Structured storage in PostgreSQL
    \item A search interface to find case information
\end{itemize}

The system runs entirely using Docker containers for frontend, backend, and database.

\newpage

%========================
% 2. EXTERNAL INTERFACE REQUIREMENTS
%========================
\section{External Interface Requirements}

\subsection{User Interface}
The system includes:
\begin{itemize}
    \item \textbf{Upload Page:} Allows users to select and upload a PDF.
    \item \textbf{Search Page:} Allows users to search by case ID, name, or keywords.
    \item \textbf{Case Detail Page:} Displays metadata extracted from documents.
    \item \textbf{Navigation Bar:} Provides access to Home, Upload, and Search.
\end{itemize}

\subsection{Software Interfaces}
\begin{itemize}
    \item \textbf{Frontend → Backend:} REST API using JSON.
    \item \textbf{Backend → Database:} PostgreSQL using environment variables.
    \item \textbf{Backend → Filesystem:} Handles uploaded PDF temporary storage.
    \item \textbf{Docker Network:} All services communicate through internal Docker networking.
\end{itemize}

\subsection{Hardware Interfaces}
None. The system operates inside virtualized Docker containers.

\subsection{Communication Interfaces}
\begin{itemize}
    \item HTTP communication through ports exposed by Docker.
    \item Localhost access for frontend and backend.
\end{itemize}

\newpage

%========================
% 3. SYSTEM REQUIREMENTS
%========================
\section{System Requirements}

% ---- FUNCTIONAL REQUIREMENTS ----
\subsection{Functional Requirements}

\subsubsection*{FR1: Document Upload}
\begin{itemize}
    \item Users shall be able to upload PDF files through the Upload page.
    \item The system shall validate PDF format before processing.
\end{itemize}

\subsubsection*{FR2: Metadata Extraction}
\begin{itemize}
    \item The system shall extract case ID, officer names, party names, and report date.
    \item Extraction failures shall return meaningful error messages.
\end{itemize}

\subsubsection*{FR3: Database Storage}
\begin{itemize}
    \item Extracted metadata shall be stored in PostgreSQL with a unique ID.
    \item Duplicate file uploads shall be prevented or flagged.
\end{itemize}

\subsubsection*{FR4: Search Functionality}
\begin{itemize}
    \item Users shall search stored cases by ID, names, or keywords.
    \item Matching results shall be returned in tabular format.
\end{itemize}

\subsubsection*{FR5: Case Detail View}
\begin{itemize}
    \item The system shall display full metadata for any selected record.
\end{itemize}

% ---- NON-FUNCTIONAL REQUIREMENTS ----
\subsection{Non-Functional Requirements}

\subsubsection*{NFR1: Performance}
\begin{itemize}
    \item Metadata extraction shall complete within 5 seconds per document.
    \item Search queries shall return results within 2 seconds.
\end{itemize}

\subsubsection*{NFR2: Usability}
\begin{itemize}
    \item The system shall require minimal user training.
    \item Navigation shall remain simple for non-technical staff.
\end{itemize}

\subsubsection*{NFR3: Reliability}
\begin{itemize}
    \item The system shall run even if one Docker container temporarily restarts.
    \item All services must start consistently using \texttt{docker-compose up}.
\end{itemize}

\subsubsection*{NFR4: Security}
\begin{itemize}
    \item Uploaded case documents must not be accessible outside the system.
    \item Data must not be sent to any third-party APIs.
\end{itemize}

\subsubsection*{NFR5: Compatibility}
\begin{itemize}
    \item System shall run on Windows, MacOS, and Linux using Docker Desktop.
    \item Frontend must support Chrome, Safari, and Edge.
\end{itemize}

\newpage

%========================
% 4. LEGAL AND ETHICAL CONSIDERATIONS
%========================
\section{Legal and Ethical Considerations}

\subsection{Data Storage and Privacy}
\begin{itemize}
    \item Case metadata may include sensitive information such as officer names and report details.
    \item All data is stored locally and not sent to cloud services.
    \item Uploaded PDFs are never shared outside the testing environment.
\end{itemize}

\subsection{Ethical Use of Document Processing}
\begin{itemize}
    \item Incorrect metadata extraction must not misrepresent case details.
    \item Users must be informed when extraction is incomplete.
\end{itemize}

\subsection{Compliance Considerations}
\begin{itemize}
    \item Project uses simulated test data only—no real case files.
    \item System must follow FERPA and academic data policies.
\end{itemize}

\newpage

%========================
% 5. GLOSSARY
%========================
\section{Glossary}

\begin{longtable}{|>{\centering\arraybackslash}m{3cm}|
                      >{\arraybackslash}m{9cm}|}
    \hline
    \textbf{Acronym} & \textbf{Definition} \\
    \hline
    UI & User Interface \\ \hline
    API & Application Programming Interface \\ \hline
    DB & Database \\ \hline
    SRS & Software Requirements Specification \\ \hline
    SDD & Software Design Document \\ \hline
\end{longtable}

\end{document}

